---
title: "Fragile Families Data Cleaning and Analysis"
author: "Emily Halford"
date: "9/18/2020"
output: html_document
---

## Loading Packages

```{r setup, include=FALSE}
library(tidyverse)
library(haven)
library(geepack)
library(lme4)
```

## Loading and Cleaning

The following code loads and cleans data from Years 9 and 15 of the Fragile Families study. Variables are given meaningful, consistent variable names, and are recoded in a binary fashion. A "time_order" variable is also created so that the data can be sorted properly in the analysis step. 

```{r load_data}

year_9 = read_sas("./data/FF_wave5_2020v2_SAS.sas7bdat") %>% 
  select(idnum, k5g2g, k5f1l, k5f1j) %>% 
  rename("feel_sad" = "k5g2g",
         "tobacco" = "k5f1l",
         "alcohol" = "k5f1j") %>% 
  filter(
    tobacco == 1 | tobacco == 2,
    alcohol == 1 | alcohol == 2,
    feel_sad == 0 | feel_sad == 1 | feel_sad == 2 | feel_sad == 3
  ) %>% 
  mutate(
    tobacco = ifelse(tobacco == 1, 1, 0),
    alcohol = ifelse(alcohol == 1, 1, 0),
    feel_sad = ifelse(feel_sad == 0, 0, 1),
    time_order = 1
  )


year_15 = read_sas("./data/FF_wave6_2020v2_SAS.sas7bdat") %>% 
  select(idnum, k6d2n, k6d40, k6d48) %>% 
  rename("feel_sad" = "k6d2n",
         "tobacco" = "k6d40",
         "alcohol" = "k6d48") %>% 
  filter(
    tobacco == 1 | tobacco == 2,
    alcohol == 1 | alcohol == 2,
    feel_sad == 1 | feel_sad == 2 | feel_sad == 3 | feel_sad == 4
  ) %>% 
  mutate(
    tobacco = ifelse(tobacco == 1, 1, 0),
    alcohol = ifelse(alcohol == 1, 1, 0),
    feel_sad = ifelse(feel_sad == 4, 0, 1),
    time_order = 2
  )

fragile_families = rbind(year_9, year_15) %>% 
  mutate(
    idnum = as.numeric(idnum)
  )

fragile_families = 
  fragile_families[
  with(fragile_families, order(idnum)),
]

```

## Analysis

The following code runs a simple logistic regression model (for comparative purposes), a generalized estimating equations model, and a multilevel model.

```{r analysis}

## Simple logistic regression
glm(formula = feel_sad ~ tobacco + alcohol, family = binomial, data = fragile_families) %>% 
  broom::tidy()

## Generalized estimating equations
geeglm(formula = feel_sad ~ tobacco + alcohol, family = binomial, id = idnum, data = fragile_families,
       waves = time_order, corstr = "independence") %>% 
  broom::tidy()

## Multilevel modeling
mlm = summary(glmer(formula = feel_sad ~ tobacco + alcohol + (1 | idnum), data = fragile_families, family = binomial)) 

mlm$coefficients

```
