---
title: "Global School-Based Student Health Survey Data Cleaning and Analysis"
author: "Emily Halford"
date: "9/18/2020"
output: html_document
---

## Loading Packages

```{r setup, include=FALSE}
library(tidyverse)
library(haven)
library(lme4)
library(gee)
```

## Loading and Cleaning

The following code loads and cleans data from students in Indonesia and Bangladesh that was collected as part of the WHO's Global School-Based Student Health Survey. Variables are given meaningful, consistent variable names, and are recoded in a binary fashion. A "country" variable is also created so that students' responses can be clustered by country in the analysis stage. 

```{r load_data}

indonesia = read_sas("./data/IOH2007_public_use.sas7bdat") %>% 
  select(q21, q25, q27) %>% 
  rename(
    "bullied" = "q21",
    "suicidal_thoughts" = "q25",
    "friends" = "q27"
  ) %>% 
  mutate(
    country = 1,
  )

bangladesh = read_sas("./data/bdh2014_public_use.sas7bdat") %>% 
  select(q20, q24, q27) %>% 
  rename(
    "bullied" = "q20",
    "suicidal_thoughts" = "q24",
    "friends" = "q27"
  ) %>% 
  mutate(
    country = 2
  ) 

survey = rbind(indonesia, bangladesh) %>% 
  mutate(
    suicidal_thoughts = as.numeric(suicidal_thoughts),
    friends = as.numeric(friends),
    bullied = as.numeric(bullied),
    suicidal_thoughts = ifelse(suicidal_thoughts == 1, 1, 0),
    friends = ifelse(friends == 1, 0, 1),
    bullied = ifelse(bullied == 1, 0, 1)
  ) %>% 
  drop_na()

```

## Analysis

The following code runs a simple logistic regression model (for comparative purposes), a generalized estimating equations model, and a multilevel model.

```{r analysis}

## Simple logistic regression
glm(formula = suicidal_thoughts ~ bullied + friends, family = binomial, data = survey) %>% 
  broom::tidy()

## Generalized estimating equations
gee = gee(suicidal_thoughts ~ bullied + friends, data = survey, id = country, family = binomial, corstr = "independence")

summary(gee)

## Multilevel modeling
mlm = summary(glmer(formula = suicidal_thoughts ~ bullied + friends + (1 | country), data = survey, family = binomial)) 

mlm$coefficients

```

